Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2014-02-21 BackMatter/paper.tex
daily works on Raman and seeded growth

>>>>

Concentration of charge carrier $n$ is related to gate voltage $V_g$ by:
\[
n = \frac{\epsilon_0 \epsilon V_g}{ed}
\[
where $\epsilon_r = \epsilon_0 \epsilon$ is dielectric constant of gate materials.

massless relativistic chiral particles, Klein paradox, 100\% tunneling and extreme high mobility.

\ce{SiO_x}-Si, \ce{WS2} absorption coefficient $10^{-7}m^{-1}$, mean free path of photo-excited charge carriers 1 $\mu m$. the wave vector of photon is considerably small than size of BZ, therefore The wave vector of phonon in Raman scattering usually close to zero.

ref M. Cardona. Light Scattering in Solids II,. Springer, Berlin, 1982

Multiple phonon scattering, For two identical phonons, the corresponding Raman peak in the spectrum is called an overtone of the peak from the corresponding one-phonon process. And the wave vector conservation rule is automatically filled, therefore the phonon involved is not limited to BZ center anymore.
\[
I(G) \approx \sum_k \frac{\langle f|H_M|b\rangle \langle b|H_{ep}|a\rangle \langle a|H_M|i\rangle}{(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma)(E_p - E_k^{\pi *}- E_k^{\pi}-i\gamma- \hbar\Omega_{G})}
\]

the average distance travelled by an excited electron-hole pair before combination $l=\nu_F/\omega_D=4nm$.

Confocal Raman spectrometer:to obtain Raman spectrum in a specific depth of sample. Edge filter to cut off Rayleigh emission.

resolution $d= 1.22 \lambda/NA$,

\section{vocabulary}

in reciprocal space, primitive cell, a sketch of device, a decisive role. anchors,

### 2014-02-21 ch-tms/Seeded_growth_draft.tex
daily works on Raman and seeded growth

\ce{WS2}-\ce{WO_x} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs (Fig.~\ref{fig0}). Tungsten trioxides NWs were synthesized by a seeded growth approach in a home-built CVD apparatus, which has been successfully employed to prepare \ce{TiO2}, \ce{WO3}\cite{Zhang2010}, \ce{MoO3} etc nanomaterials. The seeded growth details are provided in supporting information. The as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim100$mg sulfur (99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}. After pumping down, the reaction chamber was flushed two times to expel residual air. Then the furnace was heated to 750 \si{\degreeCelsius} in 30 minutes, held for 15 minutes, and allowed to naturally cool down to room temperature. During entire growth process, 30 sccm Ar was used as carrier flow.

@@

The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM, JEOL JSM-6480) and the associated energy dispersive X-ray spectroscopy unit(EDS, Oxford Instrument INCA). Crystal structures were characterized using X-ray diffraction (PANXpertX’pert Pro MRD with Cu K$\alpha$ line at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 LaB6 operated at 200kV). A Raman microscope setup (Horiba Scientific, Labram HR800) were used to detect Raman spectra.

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into acetone solution, and dipped onto PDMS () support. A micromanipulator was used to pick up the longer core-shell NWs and to transfer them onto TEM grids. The NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were examined under Raman.

\FloatBarrier

@@

%fig TEM showing CS planes

% fig Raman TEM

%

\subsection{Photocatalytic}

\clearpage
\bibliographystyle{unsrtnat}
\bibliography{\bibpath/ECD,\bibpath/tungsten_newandgood,\bibpath/ACSnano,\bibpath/tungsten_old,\bibpath/Raman,\bibpath/Molybdenum,\bibpath/tungsten_cl}

@@

\clearpage
\begin{table}[htb]
\centering
\caption{Source of figures }\label{tab:sof}
\begin{tabular}{l|c|c|r}
\hline
No of Fig & sub index & sample date & remarks\\
\hline
1        & a & 013113 & 500 \\
1        & b & 012913 & 600 \\
1        & c & 020413 & 650 \\
1        & d & 013013 & 750 \\
\hline
2       & a & 012913 & 1sccm \\
2       & b & 020513 & 2sccm \\
2       & c & 020613 & 3sccm \\
2       & d & 021113 & 10sccm \\
\hline
3       & a & 012913 &  3N\\
3       & b & 042313 &  3N5\\
3       & c & 041013 &  4N5\\
3       & d & 041113 &  5N\\
\hline
4       & a & 021513 &  8mm-x500\\
4       & a inset & 021513 &  8mm-x10k\\
4       & b & 021513 &  13mm-x500\\
4       & b inset & 021513 &  13mm-x10ka\\
\hline
5   &   xrd & 021513 & \\
\hline
6  & raman & 060313 or 021513 & \\
\hline
7 & TEM & 060413 &
\end{tabular}
\end{table}

>>>>

\ce{WS2}-\ce{WO_x} core-shell NWs were synthesized using direct sulfurization of \ce{WO3} NWs (Fig.~\ref{fig0}). Tungsten trioxides NWs were synthesized by a seeded growth approach in a home-built CVD apparatus, which has been successfully employed to prepare borides\cite{Amin2009a}, titanium oxide\cite{Amin2007}, tungsten oxides\cite{Zhang2010} and \ce{MoO3}. The seeded growth details are provided in supporting information. The as-grown \ce{WO3} NWs were loaded into the center of heating furnace, and $\sim200$mg sulfur (Alfa Aesar 10785, 99.5\%) was positioned just outside the upstream edge of furnace, where the maximum temperature was about 240 \si{\degreeCelsius}. After pumping down, the reaction chamber was flushed two times to expel residual air. A cold trap filled with liquid nitrogen in downstream was used to collect possible sulfur precipitation. Then the furnace was heated to 750 \si{\degreeCelsius} in 30 minutes, held for 15 minutes, and allowed to naturally cool down to room temperature. During entire growth process, 30 sccm Ar was used as carrier flow.

@@

The morphology and composition of the as-synthesized samples were analyzed by scanning electron microscopy (SEM, JEOL JSM-6480) and the associated energy dispersive X-ray spectroscopy unit(EDS, Oxford Instrument INCA). Crystal structures were characterized using X-ray diffraction (PANXpertX’pert Pro MRD with Cu K$\alpha$ line at $\lambda$=1.5418\AA) and transmission electron microscopy (TEM, JEOL JEM-2100 \ce{LaB6} operated at 200kV). A Raman microscope setup (Horiba Scientific, Labram HR800) were used to detect Raman spectra. The spectra was acquired using 532 nm laser (0.3 mW) and 200 seconds acquisition time.

To perform TEM-Raman integrated study, the core-shell specimen was first dispersed into acetone solution, and dipped onto polydimethylsiloxane (PDMS) support. A micromanipulator was used to pick up the longer core-shell NWs and to transfer them onto TEM grids. The NWs were first examined using TEM to identify the \ce{WS2} layers configuration and the associated geometrical orientation. Then the core-shell NWs on TEM grids were examined under Raman.

To perform TEM-Raman integrated study, the core-shell nanowires need to be transferred to TEM grid first. So the core-shell specimens were dispersed into acetone, and then dipped onto polydimethylsiloxane (PDMS) substrate. Some long core-shell nanowires on PDMS substrate were picked up and transferred to TEM grids by using a home-built micromanipulator under optical microscope

@@

%fig TEM showing CS planes
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_tem.jpg}
\caption{HRTEM images on one core-shell nanowires showing (a) the multilayer capping and void formation in \ce{WO_x} core, and (b) uniform \ce{WS2} layers on nanowire body and CS planes formation in core region.}
\label{fig:ws2tem}
\end{figure}
% fig Raman TEM
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{ws2_coreshell_integ.jpg}
\caption{TEM-Raman integrated results on one core-shell nanowires. (a)-(c) \ce{WS2} layer number variation from bulk to 2L. (d) Associated Raman spectra with site1-3 corresponding to HRTEM images (a)-(c), respectively. (e) Multi-peak Lorentzian fitting on Raman spectrum site 3 with inset showing layer number dependent intensiteis ratio of $I_{2LA}/I_{A_{1g}}$ under 532 nm excitation.}
\label{fig:ws2ram}
\end{figure}

\FloatBarrier
\subsection{Photocatalytic}

\clearpage
\bibliographystyle{unsrtnat}
\bibliography{\bibpath/Titanium,\bibpath/VLS,\bibpath/ECD,\bibpath/tungsten_newandgood,\bibpath/ACSnano,\bibpath/tungsten_old,\bibpath/Raman,\bibpath/Molybdenum,\bibpath/tungsten_cl}

@@

\clearpage
\begin{table}[htb]
\centering
\caption{Source of figures }\label{tab:sof}
\begin{tabular}{l|c|c|r}
\hline
No of Fig & sub index & sample date & remarks\\
\hline
1        & a & 013113 & 500 \\
1        & b & 012913 & 600 \\
1        & c & 020413 & 650 \\
1        & d & 013013 & 750 \\
\hline
2       & a & 012913 & 1sccm \\
2       & b & 020513 & 2sccm \\
2       & c & 020613 & 3sccm \\
2       & d & 021113 & 10sccm \\
\hline
3       & a & 012913 &  3N\\
3       & b & 042313 &  3N5\\
3       & c & 041013 &  4N5\\
3       & d & 041113 &  5N\\
\hline
4       & a & 021513 &  8mm-x500\\
4       & a inset & 021513 &  8mm-x10k\\
4       & b & 021513 &  13mm-x500\\
4       & b inset & 021513 &  13mm-x10ka\\
\hline
5   &   xrd & 021513 & \\
\hline
6  & raman & 060313 or 021513 & \\
\hline
7 & TEM & B10, B6 &
\end{tabular}
\end{table}

### 2014-02-21 ch-tms/tms.tex
daily works on Raman and seeded growth

\textbf{\ce{MS2} films} \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details. Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated. \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2. More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm. \cite{Ennaoui1995a} grew tungsten disulfides film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow. The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity. XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating. \ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed. \citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature. This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates.\cite{Genut1992} We summarize the main results in Table~\ref{tab:ws2subs}. It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture.
% WS2 films
\begin{table}[htb]
\centering
\caption{\ce{WS2} growth on different substrates}\label{tab:ws2subs}
\begin{tabular}{lcp{1in}p{2in}}
\toprule
precursor                 & substrate &  conditions & film feature\textsuperscript{\emph{a}}  \\
\midrule
sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}\\
                          & quartz      & onset 650 \si{\degreeCelsius} & $\parallel c$ below 950 \si{\degreeCelsius}\\
                          & Mo        & onset NA          & $\parallel c$ at 1000 \si{\degreeCelsius}\\
                          & W          & onset NA           & random orientation\\
\midrule
\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ at 800 \si{\degreeCelsius}\\
\bottomrule
\end{tabular}

>>>>

\textbf{\ce{MS2} films} \citeauthor{Lee1994} studied the CVD of \ce{MoS2} by \ce{MoCl5} or \ce{MoF6} and \ce{H2S} in great details. Phase diagrams for \ce{Mo-S-Cl-H} and \ce{Mo-S-F-H} system at 1 kPa were simulated. \citeauthor{Endler1999} also investigated the solid-phase diagram for \ce{Mo-S-Cl-H-Ar} system.\cite{Endler1999} It was found pure \ce{MoS2} was main product when molar ratio of \ce{H2S}-\ce{MoCl5} exceeds 2. More important, \ce{MoS2} basal plane orientation can be parallel to substrate when the thickness was smaller than 50 nm. \cite{Ennaoui1995a} grew tungsten disulfides film using sulfurization of \ce{WO3} under \ce{N2}/\ce{H2} gas flow. The composition was found to be \ce{WS_{2.13}}, and the excess of sulfur lead to p-type conductivity. XRD peaks ratio is used as a measure of film orientation, which was found higher for film prepared without an intermediate Ni coating. \ce{Ni3S2} phase was found and surfactant-mediated epitaxy is proposed. \citeauthor{Regula1997} studied the Ni-W-S phase diagram and the role of Ni layer in promoting \ce{WS2} film growth from amorphous \ce{WS3}.\cite{Regula1997} \emph{In-situ} TEM analysis confirmed the formation of \ce{NiS_x} droplets and lateral growth of \ce{WS2} from these droplets.\cite{Regula1998} Recently, it has been shown that direct sulfurization of W coating (20nm) at 750 \si{\degreeCelsius} on \ce{SiO2}-Si can also produce \ce{WS2} film.\cite{Shanmugam2012a} However, the film is of bulk in nature. This could be explained by the study of \citeauthor{Genut1992} towards \ce{WS2} growth on various substrates.\cite{Genut1992} We summarize the main results in Table~\ref{tab:ws2subs}. It was found that the \ce{WS2} nucleate from an amorphous \ce{WS3} phase and the substrate has a critical role in determining both the reaction onset temperature and the texture. The adhesion of tungsten to quartz was found to be much stronger than to glass. And oxygen-containing species such as \ce{H2O} or OH tend to cause \ce{WS2} basal plane perpendicular to substrate. 
% WS2 films
\begin{table}[htb]
\centering
\caption{\ce{WS2} growth on different substrates}\label{tab:ws2subs}
\begin{tabular}{lcp{1in}p{2in}}
\toprule
precursor                 & substrate &  conditions & film feature\textsuperscript{\emph{a}}  \\
\midrule
sputtered W + \ce{H2S}   & glass      & onset 400 \si{\degreeCelsius} & $\perp c$ at 500 \si{\degreeCelsius}, metastable \ce{WS3} found\\
                          & quartz      & onset 650 \si{\degreeCelsius} & $\parallel c$ below 950 \si{\degreeCelsius}\\
                          & Mo        & onset NA          & $\parallel c$ at 1000 \si{\degreeCelsius}\\
                          & W          & onset NA           & random orientation\\
\midrule
\ce{WO_x} + \ce{H2S}    & quartz      & onset 500 \si{\degreeCelsius} & predominantly $\perp c$ after 800 \si{\degreeCelsius}\\
                        & Mo        & onset NA          & $\parallel c$ dominant\\
                        & W       & onset NA          & random orientation\\
\bottomrule
\end{tabular}
